---
output:
  html_document:
    css: C:/Users/arosner/Desktop/custom2.css
    fig_height: 8
    fig_width: 10
    self_contained: yes
    theme: null
---
# Setting up data using headwaters package
## Shenandoah example
## ALR 2014-8-7

### Load headwaters package
```{r load pkg}

library(devtools)
install_github(repo = "headwaters", username = "anarosner")
library(headwaters)

```

###Temporarily, load datat that will later on be contained in package data
```{r temp to load pkg data}

#Everything in the package's data dir *should* load using load_all, or explicitly using load_data.  
#But, that's not working yet... this is a temp fix
setwd("C:/ALR/Models/headwaters")
for (i in list.files(path = "./data"))
     load(file.path("data",i), verbose = T )

```


### Specify file locations
```{r file locations}
model.dir<-"C:/ALR/Models/headwaters_sdoah"
buffer.file<-"park_coast_buffer"
# buffer<-readShapePoly(file.path(model.dir,"sdoah_inputs",buffer.file))
catchment.file<-"C:/ALR/Data/StreamData/NHDplus/NHDPlusCatchment/sdoah/Catchment"
```

### Load flow gages
```{r load gages, cache=TRUE}
#Retrieve gages
g.spatial<-gage.retrieve(buffer.file = file.path(model.dir,"sdoah_inputs",buffer.file),temp.dir = file.path(model.dir,"temp"),log.dir = file.path(model.dir,"logs") )

#Plot gages
plot(g.spatial,col="red",pch=16)
# plot(buffer,add=T,border="red")
plot(states.spatial,add=T)

#Place gages into NHDplus catchments
g.spatial<-gage.place.nhdplus(gages.spatial = g.spatial, catchment.file = catchment.file)

#Trace dams upstream
#   (not using basin characteristics impoundments, because don't have that processed for sdoah)
g.spatial<-gage.trace.dams(gages.spatial = g.spatial)
nrow(g.spatial) #number including dams
g.spatial<-gage.filter.dams(gages.spatial = g.spatial)
nrow(g.spatial) #number excluding dams
plot(g.spatial,col="blue",pch=16, add=T)

#Load basin characteristics
g.spatial<-gage.load.char(gages.spatial = g.spatial, basin.char.file = file.path(model.dir,"sdoah_inputs","shenandoahUpstreamStats2.RData"))


#Place gages into weather grid polygons 
g.spatial<-gage.place.weather.grid( gages.spatial=g.spatial, plot=T )

#View sample of gage info
head(g.spatial@data[!is.na(g.spatial$forest),])

```

```{r junk, eval=FALSE, echo=FALSE, results='hide'}
#Housekeeping
rm(catchments, plusflow)
gc(verbose = T)

```



### Load flow observations
```{r load flow, cache=TRUE}

#Limit to gages that have basin data for sdoah
#  as it turns out, only 3 gages have basin info, so it should make for a nice, quick demonstration
g.spatial<-g.spatial[!is.na(g.spatial$forest),]


#Load/calculate/aggregate flow data for seasonal and annual timesteps
q.matrices<-flow.retrieve( gages.spatial = g.spatial, 
                          periods = c("seasonal","annual"), log.dir = file.path(model.dir,"logs") )

#View sample of flow data
q.matrices[["seasonal"]][30:40,3,]
q.matrices[["seasonal"]][30:40,,1]
q.matrices[["seasonal"]][130:140,,1]
q.matrices[["annual"]][25:40,,1]

```

###Create weather grid polygons from file contents
```{r create weather grid}
#Will only need to do this very occassionally, when adding a new geographic region,
#    and it takes a while
#    so I'm going to skip it for this markdown
# weather.grid.poly <- weather.grid.create( regions=c("east","ohio") )
```


### Load weather observations
```{r load weather observations, cache=TRUE}


#Load/calculate/aggregate weather data for seasonal and annual timesteps
w.matrices <- weather.retrieve(gages.spatial=g.spatial, periods=c("seasonal","annual"))


tail(w.matrices[["seasonal"]][,1,])
tail(w.matrices[["seasonal"]][,,1])
tail(w.matrices[["annual"]][,,1])

```

### Merge gage (basin char and drainage area), flow, and weather
```{r merge and melt basin weather and flow into 2d format for use by models}
#Next and last thing for data prep to add to package...
```


###Footnotes, take a look at r version and packages used
```{r sessionInfo}

print(sessionInfo()) 

```


###Footnotes, look at inventory of objects created
```{r lsobjects}

ls.objects()

```

